Draft of paper

### 2024-12-08 Paper draft/draft.tex
End of problem formulation

>>>>

The system is compliant with the assumptions of \textbf{Lemma 2} in \cite{css-extended} that allow us to define the following expressions regarding the equilibrium points $\left( x_*, u_*, \nu_*, \omega_* \right)$ of the system and controller given $x_*$, defining the matrices:

\begin{equation}
    \begin{aligned}
         R &= (\Id - N_{\nu \omega})^{-1}\\
         R_{\omega} &= N_{u x} + N_{u \omega} R N_{\nu x}\\
         R_b &= N_{u \omega} R N_{\nu b} + N_{u b}
    \end{aligned}
\end{equation}

With $N_{\nu \omega}$ always invertible due to its lower triangular structure. We express:

\begin{equation}
  \begin{aligned}
    u_* &= R_{\omega} x_* + R_b\\
    \nu_* &= R N_{\nu x} x_* + R N_{\nu b}\\
    \omega_* &= \nu_*
  \end{aligned}
\end{equation}

The equilibrium state $x^*$ needs some further discussion since the expression to retrieve it is no longer explicit due to the non-linearity $\Phi$. We can retrieve the vector using a numerical solver that minimizes the following expression for a given disturbance $\bar{d}$:

\begin{equation}
  (A + B R_{\omega} - \Id) x_* + C \Phi(E x_*) + D \bar{d} + B R_b = 0
\end{equation}
